2.3 Prob Model for PCR Positivity Estimation

### 2024-04-25 2_scripts/2.3 Prob Model for PCR pos.qmd
Minor updates on figures for AABB conference

p03.3
```

@@

#### 3.5.3 Panel C: rolling incidence fig

>>>>

p03.3
```
The gap between CBS and APL seropositivity estimates for October 2023 was X% using raw seropositivity, Y% after transforming CBS to Abbott, and Z% after transforming APL to Roche.

```{r}
# How gaps were calculated: 
# X: Oct 2023, btw raw CBS & APL, Y: APL vs transformed CBS, Z: CBS vs transformed APL
tb_alberta %>%
  select(data, samplemonth, prop, raw) %>%
  .[.$samplemonth == as.yearmon("Oct 2022"),] %>%
  mutate(X = .$prop[4] - .$prop[1]) %>%
  mutate(Y = .$prop[3] - .$prop[1]) %>%
  mutate(Z = .$prop[4] - .$prop[2])
```

@@

#### 3.5.3 Panel C: rolling incidence fig
```{r}
## recorder the dataset, relevel inf variable
tb_melt_2$inf.f<-as.factor(tb_melt_2$inf)
tb_melt_2<-transform(tb_melt_2, 
                     inf.f = factor(inf.f, levels = c("ever_inf", "less_9_month",
                                                     "less_6_month", "less_3_month"))
)
# replace with friendly name for figuers
levels(tb_melt_2$inf.f)<-c("Ever infected", "Infected <9 months ago",
                           "Infected <6 months ago", "Infected <3 months ago")
## make figures p07
p07<-tb_melt_2 %>%
  ggplot(aes(x=samplemonth, y=prop, group=data, colour=data)) +
  geom_point() +
  geom_line()  +
  theme_bw()   +
  xlab("Time of Sample Collection") + 
  ylab("Rolling Incidence Proportion") +
  scale_colour_manual("", values = c("red", "blue"))
p07

# add facet names
p07<-p07 + facet_wrap(~inf.f, nrow=1) +
    theme(axis.text.x = element_text(angle = 30, vjust=0.8, hjust=0.8))
p07
```

#### 3.5.4 Make all three figures into one
```{r}
# use cowplot package
p08.upper<-cowplot::plot_grid(p03.5 + xlab ("") + ylab("Seroprevalence"), 
                              p03.3 + xlab ("") + ylab(""), nrow=1,
                              labels = c("A", "B"))

png(file="../4_output/figs/Fig.X1 AABB Conference.png", 
    width=2400, height=1800, res=300)
cowplot::plot_grid(p08.upper, p07 + theme(legend.position = c(0.95, 0.93),
                                          legend.background = element_blank()),
                   labels = c("","C"), ncol=1, rel_heights = c(1, 1))
dev.off()
```
